---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---



## Defining the Question
A Kenyan entrepreneur has created an online cryptography course and would want to advertise it on her blog. She currently targets audiences originating from various countries. In the past, she ran ads to advertise a related course on the same blog and collected data in the process. She would now like to employ your services as a Data Science Consultant to help her identify which individuals are most likely to click on her ads. 


## Metric for Success
The project will be successful upon identifying which individuals are most likely to click on the ads


## Experimental Design

Installing the necesary packages
Loading the libraries
Reading the dataset
Data cleaning
Exploratory Data Analysis

##Loading Libraries

```{r}


library(data.table)

##Load our dataset
data <- fread('advertising.csv')

#preivew the first 6 rows
head(data)

#find out the structure of the dataset
str(data)

#dimensions of the dataset
dim(data)



```




### Cleaning our dataset
```{r}
#checking if there is any null values
colSums(is.na(data))

#checking for duplicates
duplicateddata<- data[duplicated(data),]
duplicateddata
#no duplicates found since the table is empty

#rows where there were no duplicates
data<- data[!duplicated(data),]
data
dim(data) #as seen earlier no duplicated rows
```



## Checking for ouliers in various columns
```{r}
boxplot(data$`Daily Time Spent on Site`) # no outliers
boxplot(data$Age) 
#no outliers
boxplot(data$`Area Income`) 
#outliers found
boxplot(data$`Daily Internet Usage`) # no outliers

#producing the outliers in vector formart
boxplot.stats(data$`Area Income`)$out


#place a variable to the outliers in the are income column
outliers<-boxplot.stats(data$`Area Income`)$out
outliers

#assign the colume with the outlier a vaiable
area_income<-data$`Area Income`

#eliminating the outliers in the area_income column
newdata<-area_income[!area_income %in% boxplot.stats(area_income)$out]

str(newdata)
```




## Exploratory Data Analysis
```{r}
#average time spent on the site
average_time<-mean(data$`Daily Time Spent on Site`)
average_time  # 65 units of time spent on the site

#average internet usage
average_internet<-mean(data$`Daily Internet Usage`)
average_internet # 180

#frequency of the daily time spent on the internet
hist(data$`Daily Time Spent on Site`)

#frequency of the daily internet usage
hist(data$`Daily Internet Usage`)

#range of time spent on the site
range(data$`Daily Time Spent on Site`) #32.60 91.43
```


```{r}
#assigning variables to columns
internet_usage<-data$`Daily Internet Usage`
time_spent<- data$`Daily Time Spent on Site`

cov(internet_usage, time_spent) #360.9919: indicates a positive linear relationship btn the two variables

cor(internet_usage, time_spent) #0.5186585 : indicates a average linear correlation
```


### Scatter plot

```{r}
plot(internet_usage, time_spent, xlab = "Daily internet usage", ylab = "Daily time spent on the internet")
 ```
```


 

### Grouped Bar Plot
```{r}

counts <- table( data$Male, data$`Clicked on Ad`)

barplot(counts, main="Gender Distribution by Clicking the ad",
        xlab="Clicked on ad", col=c("darkblue","red"),
        legend = rownames(counts), beside=TRUE)
```





```{r}
counts # majority of the gender that clicked the add was female where 269 female clicked the ad #while 231 male never clicked the ad
```


```{r}
#load the dplyr package
library(dplyr)
head(data)

#filter the data where to have only those people who clicked on the ad
clicked<- filter(data, `Clicked on Ad` == 1)
head(clicked)
```

```{r}
#create a table of country and how many times people from each country clicked the ad
counts3<- table(clicked$Country)
max(counts3) # Ethiopia had the highest number of people clicking the ad (7 people)
```


```{r}
mean(clicked$`Area Income`) #avearge area income of theose that clisked the ad is 48614
```



```{r}
avg_time <- mean(clicked$`Daily Time Spent on Site`)
avg_time  # an average of 53 units of time spent on the site for those who clicked
```


```{r}
avg_internet<-mean(clicked$`Daily Internet Usage`)
avg_internet # an average 145 units of of internet used for those wjo clicked on the ad
```

```R

```{r}
#distribution for the people who clicked the ad
hist(clicked$Age)
```

```{r}
avg_age<- mean(clicked$Age)
avg_age # majority of the people who clicked the ad were around 40 years of age
```



```{r}
#function for mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
clickers_mode<- getmode(clicked$Age)
clickers_mode #majority of the people who clicked were 45 years old

```{r}
boxplot(`Daily Time Spent on Site`~ Male, data = clicked, xlab= "Gender", ylab= "`Daily Time Spent on Site") #more females spent alot of time on the site

```



## Conclusion and Recomendations
```R
from the analysis:
majority of those who clicked on the ad; were female
more females spent a lot of time on the site
average age of 40
specifically 45 year olds clicked the more 
both genders had the same count of those who did not click the ad
an average of 53 units of time spent on the site for those who clicked
Ethiopia had the highest number of people clicking the ad (7 people)
an average 145 units of of internet used for those wjo clicked on the ad

```


## Implementation




```{r}
# change the label to factor data type

data$`Clicked on Ad`= factor(data$`Clicked on Ad`, levels = c(0,1))

# checking if the label variable datatype has changed

sapply(data, class)
```
## Decision Trees
```{r}

# filter our dataset to include the variables that are useful for modelling
#we exclude Ad Topic Line, Country and Timestamp because they have too many unique values.

filtered_data = data[, c(1,2,3,4,7,10)]
head(filtered_data)
```


```{r}


library(rpart)
m <- rpart(`Clicked on Ad` ~ . , 
    data = filtered_data, 
    method = "class")

# plot the decision tree
library(rpart.plot)
rpart.plot(m)


```
```{r}
pred <- predict(m, filtered_data, type = "class")
table(pred, filtered_data$`Clicked on Ad`)
```
```{r}
mean(filtered_data$`Clicked on Ad` == pred)*100
```
95.7 % accuracy is a good model but we have to take into consideration that this cld result to overfitting

## Challenge the Model
### Random Forest

```{r}
set.seed(7)

#fit the model
library(caret)
model1 <- train(`Clicked on Ad`~. ,
                data = filtered_data,
                method = "ranger")
```


```{r}

pred1 <- predict(model1, 
                 filtered_data, 
                 type = "raw")

table(pred1, filtered_data$`Clicked on Ad`)

```


```{r}
mean(filtered_data$`Clicked on Ad` == pred1)*100
```
100 % accuracy is a case of overfitting, therefore we will go with the decision trees






