---
title: "Untitled"
author: "Liz"
date: "7/18/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Definition
Kira Plastinina (Links to an external site.) is a Russian brand that is sold through a defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, Philippines, and Armenia. The brand’s Sales and Marketing team would like to understand their customer’s behavior from data that they have collected over the past year. More specifically, they would like to learn the characteristics of customer groups.

## Metrics for Success

Cluster the data to learn the characteristics of customer groups.


## Data Understanding
The dataset for this Independent project can be found here [http://bit.ly/EcommerceCustomersDataset (Links to an external site.)].  

The dataset consists of 10 numerical and 8 categorical attributes. The 'Revenue' attribute can be used as the class label.
"Administrative", "Administrative Duration", "Informational", "Informational Duration", "Product Related" and "Product Related Duration" represents the number of different types of pages visited by the visitor in that session and total time spent in each of these page categories. The values of these features are derived from the URL information of the pages visited by the user and updated in real-time when a user takes an action, e.g. moving from one page to another. 
The "Bounce Rate", "Exit Rate" and "Page Value" features represent the metrics measured by "Google Analytics" for each page in the e-commerce site. 
The value of the "Bounce Rate" feature for a web page refers to the percentage of visitors who enter the site from that page and then leave ("bounce") without triggering any other requests to the analytics server during that session. 
The value of the "Exit Rate" feature for a specific web page is calculated as for all pageviews to the page, the percentage that was the last in the session.
The "Page Value" feature represents the average value for a web page that a user visited before completing an e-commerce transaction. 
The "Special Day" feature indicates the closeness of the site visiting time to a specific special day (e.g. Mother’s Day, Valentine's Day) in which the sessions are more likely to be finalized with the transaction. The value of this attribute is determined by considering the dynamics of e-commerce such as the duration between the order date and delivery date. For example, for Valentina’s day, this value takes a nonzero value between February 2 and February 12, zero before and after this date unless it is close to another special day, and its maximum value of 1 on February 8. 
The dataset also includes the operating system, browser, region, traffic type, visitor type as returning or new visitor, a Boolean value indicating whether the date of the visit is weekend, and month of the year

## Experimental Design Taken
Problem Definition
Data Sourcing
Check the Data
Perform Data Cleaning
Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
Implement the Solution
Challenge the Solution
Follow up Question




## Load the dataset
```{r}
#read the csv file
brand <- read.csv('http://bit.ly/EcommerceCustomersDataset')
head(brand)

```
```{r}
#structure if the dataset
str(brand)
```
```{r}
#dimensions of the dataset
dim(brand)
```


```{r}
#summary statistics

summary(brand)
```


Data Cleaning

```{r}
#checking for null values

colSums(is.na(brand))
```


```{r}
# remove the null values
brand <-na.omit(brand)
dim(brand)
```
```{r}
#check for duplicates
duplicated_rows <- brand[duplicated(brand), ]
duplicated_rows
```
```{r}
#remain with the unique rowws

brand_df<- brand[!duplicated(brand),]
brand_df
```



```{r}
# checking for outliers
par(mfrow=c(3,4))
for(i in 1:10) {
  
	boxplot(brand_df[,i], main=names(brand_df)[i], col = "blue")}
```
all the columsn have outliers but we are not going to remove them as they may affect our modelling


## EXploratory Data Analysis
### Univariate Analysis


```{r}

summary (brand_df)
```

```{r}

numerical_cols<-brand_df[, c( 1,2,3,4,5,6,7,8,9,10,12,13,14,15)]
numerical_cols
str(numerical_cols)

library(Hmisc)
hist(numerical_cols)
```
majority of the columns are skewed to the right

## Bivariate Aalysis
```{r}
# a graph of revenue against months
x = brand_df$Month

y = brand_df$Revenue

counts <- table(x, y)
counts
barplot(counts, main="Month against Revenue",
  xlab="Month", col=c("pink","blue", "white", "black", "maroon", "purple","orange", "yellow", "green", "violet" ),
  legend = rownames(counts), beside=TRUE)
```
May and November have are leading in revenue generated
December, March, May, November had many customers visiting the website

```{r}
plot(brand_df$Administrative_Duration, brand_df$Informational_Duration,  ylab="Information_duration", xlab="Adminstration_duration", col= "blue" , main = 'Information against administration duration')

#
```
evidence of a week positive correlation between admin duration and information duration



```{r}

plot(brand_df$Administrative_Duration , brand_df$ProductRelated_Duration,  ylab="ProductRelated duration", xlab="Adminstration_duration", col= "blue" , main = 'Administrative against ProductRelated duration')
```
evidence of a week positive correlation between admin and product relation duration



```{r}
# finding if there is any covariance btn bounce rates and exit rates

#assign bounce rate a variable
bounce <- brand_df$BounceRates

# assign  exit rates a variable
exit <- brand_df$ExitRates



cor(bounce,exit)
```
there is a very strong positive correlation between bounce rates and exit rates

```{r}
#correlation of all the numerical columns
numerical_corr<-cor(numerical_cols)
```

```{r}
install.packages("corrplot")
library(corrplot)

corrplot(numerical_corr)
```

## Modelling


```{r}
#dropping the Revenue variable since it is  the target variable
brand_clust<- brand_df[,!(names(brand_df)%in% c("Revenue"))]

head(brand_clust)


```
```{r}
#convert weekend column into numeric
brand_clust$Weekend <- as.numeric(brand_clust$Weekend)
```




```{r}
#label encode out Month column
install.packages('CatEncoders')

library(CatEncoders)

encode = LabelEncoder.fit(brand_clust$Month)

brand_clust$Month = transform(encode,brand_clust$Month)

unique(brand_clust$Month)
```

```{r}
#label encode the Visitor's type column
encode2 = LabelEncoder.fit(brand_clust$VisitorType)

brand_clust$VisitorType = transform(encode2,brand_clust$VisitorType)

unique(brand_clust$VisitorType)
```

```{r}
#previewing the data structure of out dataset
str(brand_clust)
```
```{r}
#scale our dataset
scale(brand_clust)
```

```{r}
# Applying the K-means clustering algorithm with no. of centroids(k)=3
# ---
# 
clustering<- kmeans(brand_clust,6) 
clustering$size
```
```{r}
# Getting the value of cluster center datapoint value(3 centers for k=3)
# ---
# 
clustering$centers 
```

```{r}
# Getting the cluster vector that shows the cluster where each record falls
# ---
# 
clustering$cluster
```
```{r}
par(mfrow = c(2,2), mar = c(5,4,2,2))
```


```{r}
plot(brand_clust[c(5,7)], col = clustering$cluster)

```
## Hierachical Clustering
```{r}
#calculate the euclidean distance
brand1 <- dist(brand_clust, method = "euclidean")

#cluster the model
brand_clustered <- hclust(brand1, method = "ward.D2" )
```


```{r}
# we plot the obtained dendrogram
plot(brand_clustered, cex = 0.6, hang = -1)

```

